Constant-round Blind Classical Verification of Quantum Sampling

### 2020-08-02 preliminaries.tex
Redo some comp. indis. notations

For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
let $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ denote the trace distance between $\rho_1$ and $\rho_2$. We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\eps$.
For two distributions $f_1$ and $f_2$ over the same finite domain $X$, let $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ denote their total variation distance,
and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{TV}\leq\eps$.
We additionally denote the following for states that are only computationally indistinguishable (but might be statistically far):
\begin{definition}
\label{def:comp-indis}
    Two ensemble of states $\set{\rho_{1,\lambda}}_{\lambda\in\bbN}$ and $\set{\rho_{2,\lambda}}_{\lambda\in\bbN}$ are \emph{$\eps$-computationally indistinguishable} if for all $\BQP$ distinguishers $\mathsf{D}$ and $\lambda\in\bbN$,
    $$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$
    We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
    We drop the $\eps$ parameter when it is negligible.
    We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized states as appropriate.
    We also extend it to distributions by treating them as mixed states.
\end{definition}

@@

\begin{definition}
    \label{dfn:stats-secure-proto-sampbqp}
    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
    We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
    \begin{itemize}
        \item On public inputs $1^\lambda$, $1^{1/\eps}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
            If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem}, otherwise $z=\bot$.
        \item (Completeness):
            For all accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            security parameter $\lambda\in\bbN$,
            and $x\in\zo^{\poly(\lambda)}$,
            Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
        \item (Statistical soundness): For all cheating prover $P^*$,
            accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$,
            consider the following experiment:
            \begin{itemize}
                \item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\eps}, x)$.
                \item Define $z_{ideal}$ by
                $$\begin{cases}
                    z_{ideal}=\bot & \text{if } d=\Rej\\
                    z_{ideal}\leftarrow D_x & \text{if } d=\Acc
                \end{cases}$$.
            \end{itemize}
            It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$.
		\item (Computational soundness): \Ethan{TODO write in terms of comp. indistinguishability?}
        For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,
            define $d, z, z_{ideal}$ by the same experiment as above.
            It holds that
            $$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \eps $$
    \end{itemize}
\end{definition}

>>>>

For $n$-qubit states $\rho_1, \rho_2\in\cB^{\otimes n}$,
let $\norm{\rho_1-\rho_2}_{tr}=\frac{1}{2}\norm{\rho_1-\rho_2}_1$ denote the trace distance between $\rho_1$ and $\rho_2$. We say $\rho_1$ and $\rho_2$ are $\eps$-close if $\norm{\rho_1- \rho_2}_{tr}\leq\eps$.
For two distributions $f_1$ and $f_2$ over the same finite domain $X$, let $\norm{f_1-f_2}_{TV}=\frac{1}{2}\sum_{x\in X}\abs{f_1(x)-f_2(x)}$ denote their total variation distance,
and we say $f_1$ and $f_2$ are $\eps$-close if $\norm{f_1-f_2}_{TV}\leq\eps$.
We additionally denote the following for states that are only computationally indistinguishable (but might be statistically far):
\begin{definition}
\label{def:comp-indis}
    Two ensemble of states $\set{\rho_{1,\lambda}}_{\lambda\in\bbN}$ and $\set{\rho_{2,\lambda}}_{\lambda\in\bbN}$ are \emph{$\eps$-computationally indistinguishable} if for all $\BQP$ distinguishers $\mathsf{D}$ and $\lambda\in\bbN$,
    $$\abs{\Pr\left[\mathsf{D}(\rho_{1,\lambda})=1\right]-\Pr\left[\mathsf{D}(\rho_{2,\lambda})=1\right]}\leq\eps(\lambda).$$
    % We also denote $\eps$-computational indistinguishability by $\rho_{1,\lambda}\approx_{c, \eps}\rho_{2,\lambda}$.
    We drop the $\eps$ parameter when it is negligible.
    We extend computational indistinguishability to subnormalized states by taking the distinguisher $\mathsf{D}$ to output subnormalized states as appropriate.
    We also extend it to distributions by treating them as mixed states.
\end{definition}

@@

\begin{definition}
    \label{dfn:stats-secure-proto-sampbqp}
    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
    We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
    \begin{itemize}
        \item On public inputs $1^\lambda$, $1^{1/\eps}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
            If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$ where $m$ is given in \Cref{dfn:sampling-problem}, otherwise $z=\bot$.
        \item (Completeness):
            For all accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            security parameter $\lambda\in\bbN$,
            and $x\in\zo^{\poly(\lambda)}$,
            Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\eps}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
        \item (Statistical soundness): For all cheating prover $P^*$,
            accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$,
            consider the following experiment:
            \begin{itemize}
                \item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\eps}, x)$.
                \item Define $z_{ideal}$ by
                $$\begin{cases}
                    z_{ideal}=\bot & \text{if } d=\Rej\\
                    z_{ideal}\leftarrow D_x & \text{if } d=\Acc
                \end{cases}$$.
            \end{itemize}
            It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\eps$.
		\item (Computational soundness):
			\Ethan{tried to write in terms of indistinguishability}
        For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\eps(\lambda)=\frac{1}{\poly(\lambda)}$,
            sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$,
            define $d, z, z_{ideal}$ by the same experiment as above.
            It holds that $(d, z)$ is $\eps$-computationally indistinguishable to $(d, z_{ideal})$ over $\lambda$.
            % $$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \eps $$
    \end{itemize}
\end{definition}
